Capital in the 21st Century: Chapter 9
========================================================

### Data provenance

The data were downloaded as Excel files from: http://piketty.pse.ens.fr/en/capital21c2. 

### Loading relevant libraries and data

This document depends on the [xlsx](http://cran.r-project.org/web/packages/xlsx/index.html), [reshape2](http://cran.r-project.org/web/packages/reshape2/index.html), and [ggplot2](http://cran.r-project.org/web/packages/ggplot2/index.html) packages.


```{r loadCh0,message=FALSE}
library(ggplot2)
library(xlsx)
library(reshape2)
```

## Figures 9.1 and Supplementary Figures

These figures are based on Table TS9.1. Here we read
data from the excel file and name the data series

```{r tabTS9.1, dependson="loadCh0", message=FALSE}
## Table TS9.1
ts91 = read.xlsx("../Piketty2014FiguresTables/Chapter9TablesFigures.xlsx",sheetName="TS9.1",rowIndex=7:70,colIndex=1:8,header=FALSE)
names(ts91) = c("year","france_francs_cur","france_euros_cur", "france_euros_2013", "france_cpi", "us_dollars_cur", "us_dollars_2013", "us_cpi")
```

The caption of the table lists the sources for this table
as 

> Sources. France: file "IPP-prelevements-sociaux-avril2012.xls" 
> available on www.ipp.eu (we selected the values corresponding to January the 1st of each year; the
> complete revaluation series are given in the IPP table)
> USA: official series of Bureau of Labor Statistics (we 
> selected the values corresponding to January the 1st of 
> each year; the complete revaluation series are given in 
> the BLS file)
> (consumer price index for France et US from Piketty-Zucman 2013, 
> files France.xls et USA.xls; links frozen on 2-20-13)

Now we make Figure F9.1

```{r figF9.1, dependson="tabTS9.1", fig.width=8, fig.height=4}
f91dat <- ts91[,c("year","france_euros_2013", "us_dollars_2013")]
names(f91dat) <- c("year","France","USA")

# ggplot2 doesn't support plots with 2 y axes 
# so it only shows wages in Euros

# scale to trick the two axes plot
f91dat$USA <- f91dat$USA / 1.2
f91dat <- melt(f91dat, id.var="year")
names(f91dat) <- c("year","country","wage")

plt <- ggplot(data=f91dat,aes(x=year, y=wage,group=country)) 
plt <- plt + geom_line() + geom_point(aes(shape=country))
plt <- plt + scale_y_continuous(breaks=seq(0,10), limits=c(0,10), name="Hourly minimum wage") 
plt <- plt + scale_x_continuous(breaks=seq(1950,2015,by=5), name="")
plt <- plt + ggtitle("Figure 9.1. Minimum wage in France and the U.S., 1950-2013")
plt
```

And Figures S9.1 and S9.2

```{r figs9.1, dependson="tabTS9.1", fig.width=8, fig.height=4}
fs91dat <- ts91[,c("year","france_euros_2013", "france_euros_cur")]
names(fs91dat) <- c("year", "2013 euros", "current euros")
fs91dat <- melt(fs91dat, id.var="year")
names(fs91dat) <- c("year", "currency", "wage")

plt <- ggplot(data=fs91dat, aes(x=year,y=wage,group=currency))
plt <- plt + geom_line() + geom_point(aes(shape=currency))
plt <- plt + scale_y_continuous(name="Hourly minimum wage", limits=c(0,10), breaks=seq(0,10,by=1))
plt <- plt + scale_x_continuous(name="", limits=c(1950,2013), breaks=seq(1950,2015,by=5))
plt <- plt + ggtitle("Figure S9.1. Minimum wage in France, 1950-2013")

plt
```

```{r figs9.2, dependson="tabTS9.1", fig.width=8, fig.height=4}
fs92dat <- ts91[,c("year","us_dollars_2013", "us_dollars_cur")]
names(fs92dat) <- c("year", "2013 dollars", "current dollars")
fs92dat <- melt(fs92dat, id.var="year")
names(fs92dat) <- c("year", "currency", "wage")

plt <- ggplot(data=fs92dat, aes(x=year,y=wage,group=currency))
plt <- plt + geom_line() + geom_point(aes(shape=currency))
plt <- plt + scale_y_continuous(name="Hourly minimum wage", limits=c(0,10), breaks=seq(0,10,by=1))
plt <- plt + scale_x_continuous(name="", limits=c(1950,2013), breaks=seq(1950,2015,by=5))
plt <- plt + ggtitle("Figure S9.2. Minimum wage in USA, 1950-2013")

plt
```

