The Capital/Income Ratio over the Long Run: Chapter 5
========================================================

### Data provenance

The data were downloaded as Excel files from: http://piketty.pse.ens.fr/en/capital21c2. 

### Loading relevant libraries and data

This document depends on the [xlsx](http://cran.r-project.org/web/packages/xlsx/index.html), [reshape2](http://cran.r-project.org/web/packages/reshape2/index.html), [scales](http://cran.r-project.org/web/packages/scales/index.html), [plyr](http://cran.r-project.org/web/packages/plyr/index.html), and [ggplot2](http://cran.r-project.org/web/packages/ggplot2/index.html) packages.

```{r loadCh0,message=FALSE}
library(ggplot2)
library(xlsx)
library(reshape2)
### scales for percent of the axes
library(scales)
```

These figures are based on Table CTS4.5. Here we read data from the excel file and name the data series.

```{r tabCTS4.5, message=FALSE, cache=TRUE}
## Table CTS4.5
tab_private = read.xlsx("../Piketty2014FiguresTables/Chapter5TablesFigures.xlsx",sheetName="CTS4.5", rowIndex=6:20, colIndex=1:6, header=FALSE)
names(tab_private) =  c("year","usa", "germany", "france", "uk", "europe")
tab_private$capital_type <- as.factor("Private")

tab_national = read.xlsx("../Piketty2014FiguresTables/Chapter5TablesFigures.xlsx",sheetName="CTS4.5",rowIndex=6:20, colIndex=c(1, 7:11), header=FALSE)
names(tab_national) =  c("year","usa", "germany", "france", "uk", "europe")
tab_national$capital_type <- as.factor("National")

tab_public = read.xlsx("../Piketty2014FiguresTables/Chapter5TablesFigures.xlsx",sheetName="CTS4.5", rowIndex=6:20, colIndex=c(1, 12:16), header=FALSE)
names(tab_public) =  c("year","usa", "germany", "france", "uk", "europe")
tab_public$capital_type <- as.factor("Public")

tab_foreign = read.xlsx("../Piketty2014FiguresTables/Chapter5TablesFigures.xlsx",sheetName="CTS4.5", rowIndex=6:20, colIndex=c(1, 21:25), header=FALSE)
names(tab_foreign) =  c("year","usa", "germany", "france", "uk", "europe")
tab_foreign$capital_type <- as.factor("Net foreign")

tab <- Reduce(function(x, y) merge(x, y, all=TRUE), list(tab_private, tab_national, tab_public, tab_foreign))
```

The caption of the table lists the sources for this table as: 

> Links to PZ 2013 frozen on 8-2-2013

## Figures 5.1, and 5.2

```{r func5_1, fig.width=8, fig.height=4}
run51 = function(tab, num){
  fdat <- tab[,c("year","capital_type","usa","europe")]
  names(fdat) <- c("year","capital_type", "United States","Europe")
  
  # Make the data long for stacking
  fdat <- melt(fdat, id.vars=c("year", "capital_type"))
  names(fdat) <- c("year", "capital_type", "region", "percent")
  
  qplot(year, percent, data=fdat, geom="path", colour=region, xlab="Year", ylab="Value of private and public capital (% national income)") + 
    scale_y_continuous(labels = percent, limits = c(0, 8)) +
    ggtitle(paste0("Figure ", num, ". Private and public capital: Europe and America, 1870-2010")) +
    theme(legend.position="bottom", legend.background = element_rect(fill="transparent")) +
    scale_x_continuous(breaks = seq(1870, 2010, by=20))
}
```

```{r figF5_1, dependson="tabTS5.1", fig.width=8, fig.height=4}
run51(tab, num = "5.1")
```

```{r figF5_2, dependson="tabTS5.1", fig.width=8, fig.height=4}
run51(tab, num = "5.2")
```

## Figure 5.3

```{r tabTS5.1, message=FALSE, cache=TRUE}
## Table TS5.1
tab = read.xlsx("../Piketty2014FiguresTables/Chapter5TablesFigures.xlsx",sheetName="TS5.1",rowIndex=5:45,colIndex=1:10,header=FALSE)
names(tab) =  c("year","us","japan", "germany", "france", "uk", "italy", "canada", "australia", "spain")
```

Let's make a function that will plot our data

```{r func5_3, fig.width=8, fig.height=4}
run53 = function(tab, num){
  fdat <- tab[,c("year","us","japan", "germany", "france", "uk", "italy", "canada", "australia", "spain")]
  names(fdat) <- c("year","United States","Japan", "Germany", "France", "Britain", "Italy", "Canada", "Australia", "Spain")
  
  # Make the data long for stacking
  fdat <- melt(fdat, id.var="year")
  names(fdat) <- c("year","country","percent")
  
  qplot(year, percent, data=fdat, geom="path", colour=country, xlab="Year", ylab="Value of private capital (% national income)") + 
    scale_y_continuous(labels = percent, limits = c(0, 8)) +
    ggtitle(paste0("Figure ", num, ". Private Capital in rich countries, 1970-2010")) +
    theme(legend.position="bottom", legend.background = element_rect(fill="transparent")) +
    scale_x_continuous(breaks = seq(1970, 2010, by=5))
}
```

Now we make Figure F5.3:

```{r figF5_3, dependson="tabTS5.1", fig.width=8, fig.height=4}
run53(tab, num = "5.3")
```