Capital in the 21st Century: Chapter 13
========================================================

### Data provenance

The data were downloaded as Excel files from: http://piketty.pse.ens.fr/en/capital21c2. 

### Loading relevant libraries and data

This document depends on the [xlsx](http://cran.r-project.org/web/packages/xlsx/index.html), [reshape2](http://cran.r-project.org/web/packages/reshape2/index.html), and [ggplot2](http://cran.r-project.org/web/packages/ggplot2/index.html) packages.


```{r loadCh13,message=FALSE}
library(ggplot2)
library(xlsx)
library(reshape2)


## Table TS13.1
ts131 = read.xlsx("../Piketty2014FiguresTables/Chapter13TablesFigures.xlsx",sheetName="TS13.1",rowIndex=5:20,colIndex=c(1,2:5),header=TRUE)
names(ts131)[1] = "Decade"
ts131m = melt(ts131,id.vars="Decade")
names(ts131m) = c("Decade","Country","TaxRevenues")


## Make Figure 13.1

```{r,dependson="loadCh13",fig.height=4,fig.width=8}
ggplot(data=ts131m, aes(x=Decade,y=TaxRevenues,colour=Country),xlim=c(1870,2010),xlab="Year",ylab="Tax Revenues (Percent National Income)") + geom_line()
```


## prettify above, edit below.

## Make Figure 1.2

This code remakes Figure 1.2. Note that in the figure in the Excel tables, the x-axis is not evenly spaced, so the figure looks different. 

```{r,dependson="loadCh0",fig.height=4,fig.width=8}
qplot(year,worldPopulation,data=ts12,fill=Country,geom="ribbon",position="stack",xlim=c(1700,2012),xlab="Year",ylab="Percent of World Population")
```

