Capital in the 21st Century: Chapter 0
========================================================

### Data provenance

The data were downloaded as Excel files from: http://piketty.pse.ens.fr/en/capital21c2. 

### Loading relevant libraries and data

This document depends on the [xlsx](http://cran.r-project.org/web/packages/xlsx/index.html), [reshape2](http://cran.r-project.org/web/packages/reshape2/index.html), and [ggplot2](http://cran.r-project.org/web/packages/ggplot2/index.html) packages.


```{r loadCh0,message=FALSE}
library(ggplot2)
library(xlsx)
library(reshape2)


## Table TS1.1a
ts11a = read.xlsx("./Piketty2014FiguresTables/Chapter1TablesFigures.xlsx",sheetName="TS1.1a",rowIndex=8:18,colIndex=c(1,8:12),header=FALSE)
names(ts11a) = c("year","world","europe","america","africa","asia")
ts11a[,2:6] = ts11a[,2:6]/ts11a$world*100
ts11a=subset(ts11a,select=-world)
ts11a = melt(ts11a,id.vars="year")
names(ts11a) = c("year","Country","worldOutput")

## Table TS1.2

ts12 = read.xlsx("./Piketty2014FiguresTables/Chapter1TablesFigures.xlsx",sheetName="TS1.2",rowIndex=8:18,colIndex=c(1,8:12),header=FALSE)
names(ts12) = c("year","world","europe","america","africa","asia")
ts12[,2:6] = ts12[,2:6]/ts12$world*100
ts12=subset(ts12,select=-world)
ts12 = melt(ts12,id.vars="year")
names(ts12) = c("year","Country","worldPopulation")


## Table TS1.3

ts13 = read.xlsx("./Piketty2014FiguresTables/Chapter1TablesFigures.xlsx",sheetName="TS1.3",rowIndex=8:18,colIndex=c(1,10:14),header=FALSE)
names(ts13) = c("year","world","europe","america","africa","asia")
ts13$ea = (ts13$america + ts13$europe)/2
ts13$aa = (ts13$africa + ts13$asia)/2
ts13[,2:8] = ts13[,2:8]/ts13$world*100
ts13 = melt(ts13,id.vars="year")


```


## Make Figure 1.1

This code remakes Figure 1.1. Note that in the figure in the Excel tables, the x-axis is not evenly spaced, so the figure looks different. 

```{r,dependson="loadCh0",fig.height=4,fig.width=8}
qplot(year,worldOutput,data=ts11a,fill=Country,geom="ribbon",position="stack",xlim=c(1700,2012),xlab="Year",ylab="Percent of World Output")
```

## Make Figure 1.2

This code remakes Figure 1.2. Note that in the figure in the Excel tables, the x-axis is not evenly spaced, so the figure looks different. 

```{r,dependson="loadCh0",fig.height=4,fig.width=8}
qplot(year,worldPopulation,data=ts12,fill=Country,geom="ribbon",position="stack",xlim=c(1700,2012),xlab="Year",ylab="Percent of World Population")
```

